Poseidon Adventure

### 2019-06-14 docs/index.Rmd
pesky typos

>>>>

June 14: fixed a bug and `calc_stage2age` works better now that it is using Z, and now that Zs are in the right ballpark. Still not a perfect match to true age output.

<a href="https://sgaichas.github.io/poseidon-dev/TestCalcStage2AgeNOBA.html" target="_blank">Test stage to age calculations and compare true age output NOBA - June 14, 2019</a>
